WIDS 2024 Final Presentation

### 2024-01-12 Documents/Presentation.qmd
fixed t test in pres

-   **Wage**
    -   Our wage data was obtained through the U.S. Department of Labor and Tidy Tuesday (originally from U.S. census data).
    -   This data tracked the mean and median income nationally in the United States.
    -   Another table tracked minimum wage at the state level.

@@

-   All of our data had undergone basic cleaning before we downloaded it so all of the columns were correctly formatted and there was almost 0 NA values.
-   Each data set was pared down so that only the variables relevant to our project was completed.
-   For our house election data, the table was manipulated so that only rows of candidates who won their election remained.
    -   Other minor changes included renaming variables and recoding a few outlier observations in the `party` variable.
-   For the union data, we filtered the datasets down to not include union sectors (ex. construction-unions) and added columns to adjust for inflation.
-   For our wage data, we filtered out race, as this was outside of the scope of our study.

@@

-   Our last data manipulation was combining all of our tables into two data sets: one that stores data at a national level, and another that stores data at a state level.
-   Some of the variables were only provided at the state level so they were summarized and added to the national data set.

@@

::: columns
::: {.column width="60%"}
-   Our regression analysis shows that the south and north central regions in the United States are the main regions that have seen union membership rates and political leanings show increased correlation.
-   T-test between union and non union wages
    -   1980s: t = 22.846, df = 9.4096, p-value = 1.462e-09
        -   mean of x = 26.306; mean of y = 20.375
        -   95% CI: (5.347, 6.514)
    -   2010s: t = 22.846, df = 9.4096, p-value = 1.462e-09
        -   mean of x = 3.786; mean of y = 25.664
        -   95% CI: (3.786, 5.952)
:::

>>>>

-   **Wage**
    -   Our wage data was obtained through Kaggle that pulls data from the U.S. Department of Labor and Tidy Tuesday (originally from U.S. census data).
    -   The data obtained through Kaggle data tracked tracked minimum wage at the state level.
    -    The Tidy Tuesday data contained the mean and median income nationally in the United States.

@@

-   All of our data had undergone basic cleaning before we downloaded it so all of the columns were correctly formatted and there was almost 0 NA values.
-   Each data set was pared down so that only the variables relevant to our project was completed.
-   For our house election data, the table was manipulated so that only rows of candidates who won their election remained.
    -   Other minor changes included renaming variables and recoding a few outlier observations in the `party` variable.
-   For the union data, we filtered the data sets down to not include union sectors (ex. construction-unions).
-   For our wage data, we filtered out race, as this was outside of the scope of our study.

@@

-   Our last data manipulation was combining all of our tables into two data sets: one that stores data at a national level, and another that stores data at a state level.
-   Inflation adjusted values added to national data set.
-   Some of the variables were only provided at the state level so they were summarized and added to the national data set.

@@

::: columns
::: {.column width="60%"}
-   Our regression analysis shows that the south and north central regions in the United States are the main regions that have seen union membership rates and political leanings show increased correlation.
-   T-test between union and non union wages
    -   1980s: t = 22.846, df = 9.4096, p-value = 1.462e-09
        -   mean of x = 26.306; mean of y = 20.375
        -   95% CI: (5.347, 6.514)
    -   2010s: t = 22.846, df = 9.4096, p-value = 1.462e-09
        -   mean of x = 30.533; mean of y = 25.664
        -   95% CI: (3.786, 5.952)
:::
